Illusion Game Validation (Study 1)

### 2022-08-04 study1.Rmd
update stim

cache <- FALSE
fig.width <- see::golden_ratio(7)
fig.height <- 7

@@

best_models <- function(data) {
  models <- list()
  for(i in 1:1) {
    for(j in 1:1) {
      for(k1 in c("", "_log", "_sqrt", "_cbrt")) { 
        for(k2 in c("", "_log", "_sqrt", "_cbrt")) {  
          for(side in c("", "-side")) {
            name <- paste0("dif", k1, i, "-", "str", k2, j, side)
            print(name)
            f <- paste0("poly(Illusion_Difference", 
                        k1,
                        ", ",
                        i,
                        ") * poly(Illusion_Strength",
                        k2, 
                        ", ",
                        j, 
                        ") + (1|Participant)")

@@

parameters::parameters(model)
```

>>>>

cache <- TRUE
fig.width <- see::golden_ratio(7)
fig.height <- 7

@@

best_models <- function(data) {
  models <- list()
  for(i in 1:1) {
    for(j in 1:1) {
      for(k1 in c("", "_log", "_sqrt", "_cbrt")) { 
        for(k2 in c("", "_log", "_sqrt", "_cbrt")) {  
          for(side in c("", "-side")) {
            name <- paste0("dif", k1, i, "-", "str", k2, j, side)
            # print(name)
            f <- paste0("poly(Illusion_Difference", 
                        k1,
                        ", ",
                        i,
                        ") * poly(Illusion_Strength",
                        k2, 
                        ", ",
                        j, 
                        ") + (1|Participant)")

@@

# parameters::parameters(model)
```
